Off the beaten path: \\ Gaia reveals GD-1 stars outside of the main stream

### 2018-05-01 paper/gd1.tex
S
line

\keywords{Galaxy: halo --- dark matter --
          Galaxy: kinematics and dynamics}

@@

\figurename~\ref{fig:selection} (bottom left) shows the final sample of
candidate stream members after selecting on both proper motion and photometry.
The GD-1 stream is clearly visible in the point density of \emph{individual}
stars (the positions are not binned); this is the most pure view of the stream
to date.
This increased contrast shows that the stream extends at least another
$20^\circ$ to negative longitudes.
Furthermore, the stream reaches its highest surface density where it is the
narrowest ($\phi_1\sim-13^\circ$), which may be the location of its elusive and
fully-disrupted progenitor.
Several of the under-densities and gaps hinted at from photometric selection
(\citealt{Carlberg:2013, DeBoer:2018}) appear as striking features in this
significantly cleaner map of the GD-1 stream.
% Finally, at least two new features are visible near the stream: (1) ``the
% spur,'' stars above the main stream track (in $\phi_2$) between $-40^\circ
% \lesssim \phi_1 \lesssim -30^\circ$, and (2) ``the blob,'' stars below the main
% stream track between $-20^\circ \lesssim \phi_1 \lesssim -10^\circ$.
% We discuss each of these in more detail in \sectionname
% s~\ref{sec:results}--\ref{sec:discussion} below.
Finally, at least two new features are visible near the stream: (1) ``the
spur,'' stars above the main stream track (in $\phi_2$), and (2) ``the blob,''
stars below the main stream track, both highlighted in
\figurename~\ref{fig:selection}.
We discuss each of these in more detail in \sectionname
s~\ref{sec:results}--\ref{sec:discussion} below.

>>>>

\keywords{Galaxy: halo --- dark matter ---
          Galaxy: kinematics and dynamics}

@@

\figurename~\ref{fig:selection} (bottom left) shows the final sample of
candidate stream members after selecting on both proper motion and photometry.
The GD-1 stream is clearly visible in the point density of \emph{individual}
stars (the positions are not binned); this is the most pure view of the stream
to date.
This increased contrast shows that the stream extends at least another
$20^\circ$ to negative longitudes.
Furthermore, the stream reaches its highest surface density where it is the
narrowest ($\phi_1\sim-13^\circ$), which may be the location of its elusive and
fully-disrupted progenitor.
Several of the under-densities and gaps hinted at from photometric selection
(\citealt{Carlberg:2013, DeBoer:2018}) appear as striking features in this
significantly cleaner map of the GD-1 stream.
% Finally, at least two new features are visible near the stream: (1) ``the
% spur,'' stars above the main stream track (in $\phi_2$) between $-40^\circ
% \lesssim \phi_1 \lesssim -30^\circ$, and (2) ``the blob,'' stars below the main
% stream track between $-20^\circ \lesssim \phi_1 \lesssim -10^\circ$.
% We discuss each of these in more detail in \sectionname
% s~\ref{sec:results}--\ref{sec:discussion} below.
Finally, at least two new features are visible near the stream: (1) ``the
spur,'' stars above the main stream track (in $\phi_2$), and (2) ``the blob,''
stars below the main stream track, both highlighted in
\figurename~\ref{fig:selection}.
We discuss each of these in more detail in \S\,
\ref{sec:results}--\ref{sec:discussion} below.
